Measuring precise radial velocities and cross-correlation function line-profile variations using a Skew Normal density\thanks{Based on observations collected at the La Silla Parana Observatory, ESO (Chile), with the HARPS spectrograph at the 3.6-m telescope.}

### 2018-06-06 manuscript.tex
5.3 updates

To get CCFs affected by realistic stellar activity signals, we took the ones from Alpha Cen B used in the preceding section. To simulate a planetary signal, we then blue- or red-shifted those CCFs with the wanted amplitude, period and phase.
We first simulated several RV data sets, with always the same stellar signal, but injecting planets with parameters corresponding to the following grid:
\begin{itemize}
\item period of 3, 5, 7, 9, 11, 15, 20 , 25 and 30 days,
\item amplitude from 0.5 to 3 \ms\, by steps of 0.05\,\ms,
\item 10 different phases, evenly sampled between 0 and 2$\pi$.
\end{itemize}

For each simulation, 4500 in total, we applied the activity correction presented in Eq.~\ref{eq:RV:correction} and look for signals in the residuals using a Generalized Lomb-Scargle periodogram \citep[][]{Zechmeister-2009,Scargle-1982,Lomb-1976a}. If a signal with a p--value\footnote{estimated by bootstrap} smaller than 1\% had a period compatible with the injected planetary period considering an error of 20\%, we were estimating this signal as significant, and therefore the corresponding planet as detected. Finally, for each period, we searched for the minimum amplitude for which at least 50\% of the planets with different phases were detected. The results are shown in Fig.~\ref{fig:detection_limits}. As we can see, all the different RV estimates gives extremely similar detection limits. Therefore, we can use any of these estimates when searching for planetary signal in RV data contaminated by stellar activity.

>>>>

In order to obtain CCFs affected by realistic stellar activity signals, the CCFs from Alpha Cen B used previously were considered. 
To simulate a planetary signal, the CCFs were blue- or red-shifted with the desired amplitude, period, and phase.
Several RV data sets with the same stellar signal, but different planetary signals were injected using parameters corresponding to the following grid:
\begin{itemize}
\item period of 3, 5, 7, 9, 11, 15, 20, 25, and 30 days,
\item amplitude from 0.5 to 3 \ms\, by steps of 0.05\,\ms,
\item 10 different phases, evenly sampled between 0 and 2$\pi$.
\end{itemize}

For each of the 4500 simulations considered, the activity correction presented in Eq.~\ref{eq:RV:correction} was applied, and signals in the residuals were investigated using a Generalized Lomb-Scargle periodogram \citep[][]{Lomb-1976a, Scargle-1982, Zechmeister-2009}. 
If a signal with a p--value\footnote{The p--values were estimated using a bootstrap procedure.} smaller than 1\% had a period compatible with the injected planetary period within an error budget of 20\%, the signal was considered significant and the corresponding planet considered detected. 
Finally, for each period considered, the minimum amplitude at which at least 50\% of the planets with different phases were detected was found. The results are shown in Fig.~\ref{fig:detection_limits}. 
All three of the different RV estimators give similar detection limits. Though more investigations should be considered, these results suggest that any of the RV estimators can be used when searching for a planetary signal in RV data contaminated by stellar activity.
